D.I.A.G.R.A.M.: Development of Image Analysis for Graph Recognition And Modeling

### 2025-05-11 doc/article/article.tex

\section{Experiments}
\subsection{Dataset}
TODO

\subsection{Metrics}
TODO

\subsection{Results}
TODO

>>>>

\section{Experiments}
\subsection{Text Digitization}
In order to choose an appropriate model, some tests were done over our specific dataset employing some different, pre-made models. The average results over the dataset are shown in Table~\ref{tab:text_digitization}.

\begin{table}[htbp]
\caption{Text Distance Metrics}
\centering
\begin{tabular}{lccc}
\hline
\textbf{Model} & \textbf{Hamming} & \textbf{Cosine} & \textbf{Euclidean} \\
\hline
microsoft-trocr-small-printed & 1.392 & 0.150 & 7133 \\
microsoft-trocr-base-printed & 1.286 & 0.081 & 3594 \\
microsoft-trocr-small-handwritten & 1.346 & 0.100  & 3947 \\
microsoft-trocr-base-handwritten & --- & --- & --- \\
% Add more models as needed
\hline
\end{tabular}
\label{tab:text_digitization}
\end{table}
